---
title: "Lab_07"
format: html
editor_options: 
  chunk_output_type: console
---

```{r}

```

We will examine chick weights where chicks were fed different diets. You can use the code below and ?ChickWeight to learn about the data.

Run an ANOVA and Tukey test to assess differences in the weights between diet groups on day 21 of the study. Be sure to check model assumptions.

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Load the ChickWeight dataset
data("ChickWeight")

# Check the structure of the dataset
str(ChickWeight)

# Filter the data to focus on a specific time point (e.g., day 21)
chick_data_day21 <- ChickWeight %>% filter(Time == 21)

```

```{r}

anova <- aov(weight ~ Diet, data = chick_data_day21)
summary(anova)


tukey <- TukeyHSD(anova)
print(tukey)


plot(anova)
```

Running the above plot on the anova gives 4 different plots.

The first plot is Residual vs Fitted. This plot has a fairly flat line, so this is a good assumption and model.

The second plot is a Q-Q plot. The standardized residuals fall generally on the QQ line, so this assumption is also good.

The third and fourth plot I am a little confused by, but I know the line is supposed to be mostly flat. With real data like this it rarely is, so I believe both of these model assumptions are also good.
